### 2014-10-08 Docs/architecture/architecture.tex

>>>>

You generally won't see calls in the MAESTRO source code to these subroutines,
as there is now a special BoxLib subroutine, {\tt ml\_restrict\_and\_fill},
that takes an array of multifabs at different level, and in order calls:
(1) {\tt ml\_cc\_restriction\_c}, (2) {\tt multifab\_fill\_boundary},
(3) {\tt multifab\_physbc}, and (4) {\tt multifab\_fill\_ghost\_cells}.
These four subroutines are called in such a way to avoid extra
ghostcell filling, saving on communication time.  You can specify the
starting component, starting boundary condition component, 
the number of components, the number of ghost cells,
and whether or not you want to use the same boundary condition component
for all variables.

### 2014-10-08 Docs/networks/networks.tex

>>>>

\subsection{{\tt ignition\_chamulak}}

This network was introduced in our paper on convection in white dwarfs
as a model of Type Ia supernovae~\cite{wdconvect}.  It models 
carbon burning in a regime appropriate for a simmering white dwarf,
and captures the effects of a much larger network by setting the ash
state and energetics to the values suggested in \cite{chamulak:2008}.

\subsection{{\tt ignition\_simple}}

This is the original network used in our white dwarf convection
studies~\cite{lowMach4}.  It includes a single reaction,
$^{12}\mathrm{C}({}^{12}\mathrm{C},\gamma){}^{24}\mathrm{Mg}$, using
the rate from Caughlin and Fowler~\cite{caughlan-fowler:1988}.

\subsection{{\tt rprox}}

This is a network introduced in a paper modeling mixed H/He X-ray
bursts~\cite{xrb2}.  {\tt rprox} that has 10 species approximates hit
CNO burning, triple-$\alpha$, and rp-process breakout up through
$^{56}\mathrm{Ni}$.  Updated rates from ReacLib~\cite{ReacLib} are
used.  The overall ideas in this network are based on Appendix C of
\cite{wallacewoosley:1981}.
